Intelligent Reflecting Surface-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design

### 2020-11-30 main.tex
:art: Update layout

\documentclass[journal,12pt,onecolumn,draftcls]{IEEEtran}

@@

			\textit{Third}, we conduct numerical evaluations to demonstrate the advantage of the proposed IRS-aided SWIPT architecture. Despite the hardware limitations of the IRS that constraint the reflection elements to be frequency-flat, numerical results show significant R-E benefits of the proposed joint waveform and beamforming design. We confirmed the main observations of SWIPT, namely a dedicated power waveform is beneficial for multi-carrier transmission, and TS/PS are preferred at low/high SNR, carry on to the IRS-aided SWIPT. Moreover, new observations are that 1) the IRS should be placed close to the transmitter or the receiver for optimal performance, 2) the number of transmit antenna and IRS elements have no noticeable impact on the optimal transceiving mode (TS/PS), 3) for active beamforming, increasing the number of transmit antennas brings a linear enhancement to the SNR and a quadratic boost to the harvested DC power, 4) for passive beamforming, increasing the number of reflecting elements provides a quadratic enhancement to the SNR and a quartic boost to the harvested DC power, 5) only the waveform and splitting ratio need to be updated for the R-E boundary of narrowband transmission, 6) the adaptive (i.e. rate-dependent) passive beamforming is required for broadband transmission.

@@

			\begin{figure*}[!b]
				\hrule
				\begin{align}
					z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho) & = \beta_2\rho\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr)\nonumber\\
					& \quad + \beta_4\rho^2\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\}+6\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr).\label{eq:z_expand}
				\end{align}
				\hrule
				\begin{align}
					\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}
					& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})^*} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I},0}\boldsymbol{h},\label{eq:y_I2}\\
					\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\}
					& = \frac{3}{4}\left(\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})^*}\right)^2 = \frac{3}{4}(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I},0}\boldsymbol{h})^2,\label{eq:y_I4}\\
					\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}
					& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{P},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{P},n})^*} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},0}\boldsymbol{h},\label{eq:y_P2}\\
					\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\}
					& = \frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(\boldsymbol{h}_{{n_1}}^H\boldsymbol{w}_{\mathrm{P},{n_1}})(\boldsymbol{h}_{{n_2}}^H\boldsymbol{w}_{\mathrm{P},{n_2}})(\boldsymbol{h}_{{n_3}}^H\boldsymbol{w}_{\mathrm{P},{n_3}})^*(\boldsymbol{h}_{{n_4}}^H\boldsymbol{w}_{\mathrm{P},{n_4}})^*}\nonumber\\
					& = \frac{3}{8}\sum_{k=-N+1}^{N-1}(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},k}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},k}\boldsymbol{h})^*.\label{eq:y_P4}
				\end{align}
			\end{figure*}
		\end{subsection}

		\begin{subsection}{Rate-Energy Region}
			The achievable R-E region is defined as
			\begin{equation}
				C_{R_{\mathrm{ID}}-I_{\mathrm{EH}}}(P) \triangleq \biggl\{(R_{\mathrm{ID}}, I_{\mathrm{EH}}): R_{\mathrm{ID}} \le R, I_{\mathrm{EH}} \le z, \frac{1}{2}\left(\lVert{\boldsymbol{w}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{w}_{\mathrm{P}}}\rVert^2\right) \le P\biggr\}
			\end{equation}
			where $P$ is the average transmit power budget and the coefficient \num{1/2} converts the peak power of sine waves to the average power.
		\end{subsection}
	\end{section}

@@

				& = \frac{1}{2}{\beta_2}{\rho}(t_{\mathrm{I},0}+t_{\mathrm{P},0}) + \frac{3}{8}{\beta_4}{\rho^2} \left(2t_{\mathrm{I},0}^2 + \sum_{k=-N+1}^{N-1}{t_{\mathrm{P},k}t_{\mathrm{P},k}^*}\right) + \frac{3}{2}{\beta_4}{\rho^2}t_{\mathrm{I},0}t_{\mathrm{P},0}.\label{eq:z_irs}

@@

@@

				& \ge \frac{1}{2}(t_{\mathrm{I},0}^{(i)} + t_{\mathrm{P},0}^{(i)})(t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)}) - \frac{1}{4}(t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)})^2 - \frac{1}{4}(t_{\mathrm{I},0}^{(i)} - t_{\mathrm{P},0}^{(i)})^2\label{eq:taylor_3}

@@

@@

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=0.25\columnwidth}
				\input{assets/re_subband.tex}
			\end{adjustbox}
			\caption{Average R-E region versus $N$ for $M=1$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
			\label{fi:re_subband}
		\end{figure}

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=0.25\columnwidth}
				\input{assets/waveform_subband.tex}
			\end{adjustbox}
			\caption{WPT-optimized waveform amplitudes versus $N$ for $M=1$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
			\label{fi:waveform_subband}
		\end{figure}

@@

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=0.25\columnwidth}
				\input{assets/re_noise.tex}
			\end{adjustbox}
			\caption{Average R-E region and splitting ratio versus $\sigma_n$ for $M=1$, $N=16$, $L=20$, $B=1\,\si{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
			\label{fi:re_noise}
		\end{figure}

@@

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=0.25\columnwidth}
				\input{assets/re_distance.tex}
			\end{adjustbox}
			\caption{Average R-E region versus $d_{\mathrm{H}}$ for $M=1$, $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\mathrm{V}}=2\,\si{\meter}$.}
			\label{fi:re_distance}
		\end{figure}

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=0.25\columnwidth}
				\input{assets/path_loss.tex}
			\end{adjustbox}
			\caption{Path loss versus distance for IEEE TGn channel model D.}
			\label{fi:path_loss}
		\end{figure}

@@

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=0.25\columnwidth}
				\input{assets/re_tx.tex}
			\end{adjustbox}
			\caption{Average R-E region versus $M$ for $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
			\label{fi:re_tx}
		\end{figure}

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=0.25\columnwidth}
				\input{assets/re_reflector.tex}
			\end{adjustbox}
			\caption{Average R-E region versus $L$ for $M=1$, $N=16$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
			\label{fi:re_reflector}
		\end{figure}

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=0.25\columnwidth}
				\input{assets/scaling_tx.tex}
			\end{adjustbox}
			\caption{Average WIT SNR and WPT DC current versus $M$ for $L=20$, $N=16$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$, $d_{\mathrm{H}}=0$ and $d_{\mathrm{V}}=0.5\,\si{\meter}$.}
			\label{fi:scaling_tx}
		\end{figure}

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=0.25\columnwidth}
				\input{assets/scaling_reflector.tex}
			\end{adjustbox}
			\caption{Average WIT SNR and WPT DC current versus $L$ for $M=1$, $N=16$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$, $d_{\mathrm{H}}=0$ and $d_{\mathrm{V}}=0.5\,\si{\meter}$.}
			\label{fi:scaling_reflector}
		\end{figure}

		The number of transmit antennas $M$ and IRS elements $L$ influence the average R-E tradeoff as revealed in Fig.~\ref{fi:re_tx} and \ref{fi:re_reflector}. \textit{First,} it is observed that adding either active or passive elements benefits both information and power transmission. This is because increasing $M$ or $L$ indeed enhances the equivalent composite channel strength. \textit{Second,} the number of active and passive elements have negligible impacts on the optimal transceiving mode (TS/PS). Unlike the noise, the channel strength influences both information and power transfer, thus varying $M$ or $L$ simultaneously scales both rate and current and preserves the general trend of the R-E boundary. \textit{Third,} the passive beamforming has a larger array gain and power scaling order than the active beamforming. This behavior is more obvious in Fig.~\ref{fi:scaling_tx} and \ref{fi:scaling_reflector} that illustrate the performance of WIT and WPT only. For the active MRT beamforming, doubling $M$ brings a \SI{3}{\dB} gain at the average output SNR, corresponding to a transmit array gain of $M$ and a doubled harvester input power. Due to the rectifier nonlinearity, the output DC current ends up with a nearly four-time (\SI{12}{\dB}) increase, validating the active scaling law in the order of $M^2$ \cite{Clerckx2016a}. On the other hand, when the IRS is very close to the transmitter or the receiver, doubling $L$ can bring an SNR boost up to \SI{6}{\dB}, corresponding to a reflect array gain of $L^2$. An interpretation is that the IRS coherently combines multiple signal copies with a receive array gain $L$, then performs an equal gain reflection with a transmit array gain $L$, achieving a total gain of $L^2$. As a consequence, doubling IRS elements brings a four-fold boost on the received signal power that further amplifies the harvested DC current by 16 times (\SI{24}{\dB}), suggesting a passive scaling law in the order of $L^4$. Besides, by considering harvester nonlinearity, the proposed design brings a nearly \SI{20}{\dB} increase in the output DC current over the conventional linear perspective. These results emphasize the effectiveness of passive beamforming and the importance of modeling rectifier nonlinearity in the SWIPT system design. \textit{Fourth,} small-scale SWIPT is dominated by the active beamforming while large-scale SWIPT relies more on the passive beamforming. As shown in Fig.~\ref{fi:path_loss}, in our setup, the direct path loss $\Lambda_\mathrm{D}$ is around \SI{60}{\dB} while the auxiliary path loss product $\Lambda_{\mathrm{I}}\Lambda_R$ is over \SI{100}{\dB}. Hence, to fully exploit the R-E advantage of passive beamforming, a large number of reflecting elements are required to enhance the auxiliary channel strength. Another explanation is that the RF-chains of active antennas provide design flexibility in the frequency domain, while the frequency-flat characteristic of the IRS restricts its benefit for broadband transmission, especially when $L$ is small.
		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=0.25\columnwidth}
				\input{assets/re_irs_1mhz.tex}
			\end{adjustbox}
			\caption{Average R-E region for ideal, adaptive, fixed and no IRS over $B=1\,\si{\MHz}$ for $M=1$, $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
			\label{fi:re_irs_1mhz}
		\end{figure}

>>>>

\documentclass[journal]{IEEEtran}

@@

			\textit{Third}, we conduct numerical evaluations to demonstrate the advantage of the proposed IRS-aided SWIPT architecture. Despite the hardware limitations of the IRS that constraint the reflection elements to be frequency-flat, numerical results show significant R-E benefits of the proposed joint waveform and beamforming design. We confirmed the main observations of SWIPT, namely a dedicated power waveform is beneficial for multi-carrier transmission, and TS/PS are preferred at low/high SNR, carry on to the IRS-aided SWIPT. Moreover, new observations are that 1) the IRS should be placed close to the transmitter or the receiver for optimal performance, 2) the number of transmit antenna and IRS elements have no noticeable impact on the optimal transceiving mode (TS/PS), 3) for active beamforming, increasing the number of transmit antennas brings a linear enhancement to the SNR and a quadratic boost to the harvested DC power, 4) for passive beamforming, increasing the number of reflecting elements provides a quadratic enhancement to the SNR and a quartic boost to the harvested DC power, 5) for narrowband transmission, the optimal active and passive beamforming are fixed for a given channel, and one only need to update the waveform and splitting ratio to draw the whole R-E boundary, 6) for broadband transmission, the frequency diversity enables rate-dependent adaptive passive beamforming to control the subchannel strength distribution and improve the R-E tradeoff.

@@

				\begin{equation}
					z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho) = \beta_2\rho\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr)+\beta_4\rho^2\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\}+6\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr).\label{eq:z_expand}
				\begin{flalign}
					\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}
					& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})^*} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I},0}\boldsymbol{h},&&\label{eq:y_I2}\\
					\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\}
					& = \frac{3}{4}\left(\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})^*}\right)^2 = \frac{3}{4}(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I},0}\boldsymbol{h})^2,&&\label{eq:y_I4}
				\end{flalign}
				\begin{flalign}
					\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}
					& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{P},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{P},n})^*} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},0}\boldsymbol{h},&&\label{eq:y_P2}\\
					\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\}
					& = \frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(\boldsymbol{h}_{{n_1}}^H\boldsymbol{w}_{\mathrm{P},{n_1}})(\boldsymbol{h}_{{n_2}}^H\boldsymbol{w}_{\mathrm{P},{n_2}})(\boldsymbol{h}_{{n_3}}^H\boldsymbol{w}_{\mathrm{P},{n_3}})^*(\boldsymbol{h}_{{n_4}}^H\boldsymbol{w}_{\mathrm{P},{n_4}})^*} = \frac{3}{8}\sum_{k=-N+1}^{N-1}(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},k}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},k}\boldsymbol{h})^*.&&\label{eq:y_P4}
				\end{flalign}
			% \begin{figure*}[!b]
			% 	\hrule
			% 	\begin{align}
			% 		z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho) & = \beta_2\rho\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr)\nonumber\\
			% 		& \quad + \beta_4\rho^2\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\}+6\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr).\label{eq:z_expand}
			% 	\end{align}
			% 	\hrule
			% 	\begin{align}
			% 		\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}
			% 		& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})^*} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I},0}\boldsymbol{h},\label{eq:y_I2}\\
			% 		\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\}
			% 		& = \frac{3}{4}\left(\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})^*}\right)^2 = \frac{3}{4}(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I},0}\boldsymbol{h})^2,\label{eq:y_I4}\\
			% 		\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}
			% 		& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{P},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{P},n})^*} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},0}\boldsymbol{h},\label{eq:y_P2}\\
			% 		\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\}
			% 		& = \frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(\boldsymbol{h}_{{n_1}}^H\boldsymbol{w}_{\mathrm{P},{n_1}})(\boldsymbol{h}_{{n_2}}^H\boldsymbol{w}_{\mathrm{P},{n_2}})(\boldsymbol{h}_{{n_3}}^H\boldsymbol{w}_{\mathrm{P},{n_3}})^*(\boldsymbol{h}_{{n_4}}^H\boldsymbol{w}_{\mathrm{P},{n_4}})^*}\nonumber\\
			% 		& = \frac{3}{8}\sum_{k=-N+1}^{N-1}(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},k}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},k}\boldsymbol{h})^*.\label{eq:y_P4}
			% 	\end{align}
			% \end{figure*}

		\begin{subsection}{Rate-Energy Region}
			The achievable R-E region is defined as
			\begin{align}
				C_{R_{\mathrm{ID}}-I_{\mathrm{EH}}}(P)
				&\triangleq \biggl\{(R_{\mathrm{ID}}, I_{\mathrm{EH}}): R_{\mathrm{ID}} \le R, I_{\mathrm{EH}} \le z,\nonumber\\
				&\quad \frac{1}{2}\left(\lVert{\boldsymbol{w}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{w}_{\mathrm{P}}}\rVert^2\right) \le P\biggr\}
			\end{align}
			% \begin{equation}
			% 	C_{R_{\mathrm{ID}}-I_{\mathrm{EH}}}(P) \triangleq \biggl\{(R_{\mathrm{ID}}, I_{\mathrm{EH}}): R_{\mathrm{ID}} \le R, I_{\mathrm{EH}} \le z, \frac{1}{2}\left(\lVert{\boldsymbol{w}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{w}_{\mathrm{P}}}\rVert^2\right) \le P\biggr\}
			% \end{equation}
			where $P$ is the average transmit power budget and the coefficient \num{1/2} converts the peak power of sine waves to the average power.
		\end{subsection}
	\end{section}

@@

				& = \frac{1}{2}{\beta_2}{\rho}(t_{\mathrm{I},0}+t_{\mathrm{P},0})\nonumber\\
				& \quad + \frac{3}{8}{\beta_4}{\rho^2} \left(2t_{\mathrm{I},0}^2 + \sum_{k=-N+1}^{N-1}{t_{\mathrm{P},k}t_{\mathrm{P},k}^*}\right)\nonumber\\
				& \quad + \frac{3}{2}{\beta_4}{\rho^2}t_{\mathrm{I},0}t_{\mathrm{P},0}.\label{eq:z_irs}

@@

			% \begin{align}
			% 	R(\boldsymbol{\Phi})
			% 	& = \sum_{n=1}^{N}{\log_2\left(1+\frac{(1-\rho)\mathrm{Tr}(\boldsymbol{C}_n\boldsymbol{\Phi})}{\sigma_n^2}\right)},\label{eq:R_irs}\\
			% 	z(\boldsymbol{\Phi})
			% 	& = \frac{1}{2}{\beta_2}{\rho}(t_{\mathrm{I},0}+t_{\mathrm{P},0}) + \frac{3}{8}{\beta_4}{\rho^2} \left(2t_{\mathrm{I},0}^2 + \sum_{k=-N+1}^{N-1}{t_{\mathrm{P},k}t_{\mathrm{P},k}^*}\right) + \frac{3}{2}{\beta_4}{\rho^2}t_{\mathrm{I},0}t_{\mathrm{P},0}.\label{eq:z_irs}
			% \end{align}

@@

				& \ge \frac{1}{2}(t_{\mathrm{I},0}^{(i)} + t_{\mathrm{P},0}^{(i)})(t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)})\nonumber\\
				& \quad - \frac{1}{4}(t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)})^2 - \frac{1}{4}(t_{\mathrm{I},0}^{(i)} - t_{\mathrm{P},0}^{(i)})^2\label{eq:taylor_3}

@@

			% \begin{align}
			% 	(t_{\mathrm{I},0}^{(i)})^2
			% 	& \ge 2 t_{\mathrm{I},0}^{(i)}t_{\mathrm{I},0}^{(i-1)} - (t_{\mathrm{I},0}^{(i-1)})^2,\label{eq:taylor_1}\\
			% 	t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i)})^*
			% 	& \ge 2 \Re\left\{t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i-1)})^*\right\} - t_{\mathrm{P},k}^{(i-1)} (t_{\mathrm{P},k}^{(i-1)})^*,\label{eq:taylor_2}\\
			% 	t_{\mathrm{I},0}^{(i)} t_{\mathrm{P},0}^{(i)}
			% 	& = \frac{1}{4}(t_{\mathrm{I},0}^{(i)} + t_{\mathrm{P},0}^{(i)})^2 - \frac{1}{4}(t_{\mathrm{I},0}^{(i)} - t_{\mathrm{P},0}^{(i)})^2\nonumber\\
			% 	& \ge \frac{1}{2}(t_{\mathrm{I},0}^{(i)} + t_{\mathrm{P},0}^{(i)})(t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)}) - \frac{1}{4}(t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)})^2 - \frac{1}{4}(t_{\mathrm{I},0}^{(i)} - t_{\mathrm{P},0}^{(i)})^2\label{eq:taylor_3}
			% \end{align}

@@

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=0.9\columnwidth}
				\input{assets/re_subband.tex}
			\end{adjustbox}
			\caption{Average R-E region versus $N$ for $M=1$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
			\label{fi:re_subband}
		\end{figure}

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=0.9\columnwidth}
				\input{assets/waveform_subband.tex}
			\end{adjustbox}
			\caption{WPT-optimized waveform amplitudes versus $N$ for $M=1$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
			\label{fi:waveform_subband}
		\end{figure}

@@

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=0.9\columnwidth}
				\input{assets/re_noise.tex}
			\end{adjustbox}
			\caption{Average R-E region and splitting ratio versus $\sigma_n$ for $M=1$, $N=16$, $L=20$, $B=1\,\si{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
			\label{fi:re_noise}
		\end{figure}

@@

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=0.9\columnwidth}
				\input{assets/re_distance.tex}
			\end{adjustbox}
			\caption{Average R-E region versus $d_{\mathrm{H}}$ for $M=1$, $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\mathrm{V}}=2\,\si{\meter}$.}
			\label{fi:re_distance}
		\end{figure}

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=0.9\columnwidth}
				\input{assets/path_loss.tex}
			\end{adjustbox}
			\caption{Path loss versus distance for IEEE TGn channel model D.}
			\label{fi:path_loss}
		\end{figure}

@@

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=0.9\columnwidth}
				\input{assets/re_tx.tex}
			\end{adjustbox}
			\caption{Average R-E region versus $M$ for $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
			\label{fi:re_tx}
		\end{figure}

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=0.9\columnwidth}
				\input{assets/re_reflector.tex}
			\end{adjustbox}
			\caption{Average R-E region versus $L$ for $M=1$, $N=16$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
			\label{fi:re_reflector}
		\end{figure}

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=0.9\columnwidth}
				\input{assets/scaling_tx.tex}
			\end{adjustbox}
			\caption{Average WIT SNR and WPT DC current versus $M$ for $L=20$, $N=16$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$, $d_{\mathrm{H}}=0$ and $d_{\mathrm{V}}=0.5\,\si{\meter}$.}
			\label{fi:scaling_tx}
		\end{figure}

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=0.9\columnwidth}
				\input{assets/scaling_reflector.tex}
			\end{adjustbox}
			\caption{Average WIT SNR and WPT DC current versus $L$ for $M=1$, $N=16$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$, $d_{\mathrm{H}}=0$ and $d_{\mathrm{V}}=0.5\,\si{\meter}$.}
			\label{fi:scaling_reflector}
		\end{figure}

		The number of transmit antennas $M$ and IRS elements $L$ influence the average R-E tradeoff as revealed in Fig.~\ref{fi:re_tx} and \ref{fi:re_reflector}. \textit{First,} it is observed that adding either active or passive elements benefits both information and power transmission. This is because increasing $M$ or $L$ indeed enhances the equivalent composite channel strength. \textit{Second,} the number of active and passive elements have negligible impacts on the optimal transceiving mode (TS/PS). Unlike the noise, the channel strength influences both information and power transfer, thus varying $M$ or $L$ simultaneously scales both rate and current and preserves the general trend of the R-E boundary. \textit{Third,} the passive beamforming has a larger array gain and power scaling order than the active beamforming. This behavior is more obvious in Fig.~\ref{fi:scaling_tx} and \ref{fi:scaling_reflector} that illustrate the performance of WIT and WPT only. For the active MRT beamforming, doubling $M$ brings a \SI{3}{\dB} gain at the average output SNR, corresponding to a transmit array gain of $M$ and a doubled harvester input power. Due to the rectifier nonlinearity, the output DC current ends up with a nearly four-time (\SI{12}{\dB}) increase, validating the active scaling law in the order of $M^2$ \cite{Clerckx2016a}. On the other hand, when the IRS is very close to the transmitter or the receiver, doubling $L$ can bring an SNR boost up to \SI{6}{\dB}, corresponding to a reflect array gain of $L^2$. An interpretation is that the IRS coherently combines multiple signal copies with a receive array gain $L$, then performs an equal gain reflection with a transmit array gain $L$, achieving a total gain of $L^2$. As a consequence, doubling IRS elements brings a four-fold boost on the received signal power that further amplifies the harvested DC current by 16 times (\SI{24}{\dB}), suggesting a passive scaling law in the order of $L^4$. Besides, by considering harvester nonlinearity, the proposed design brings a nearly \SI{20}{\dB} increase in the output DC current over the conventional linear perspective. These results emphasize the effectiveness of passive beamforming and the importance of modeling rectifier nonlinearity in the SWIPT system design. \textit{Fourth,} small-scale SWIPT is dominated by the active beamforming while large-scale SWIPT relies more on the passive beamforming. As shown in Fig.~\ref{fi:path_loss}, in our setup, the direct path loss $\Lambda_\mathrm{D}$ is around \SI{60}{\dB} while the auxiliary path loss product $\Lambda_{\mathrm{I}}\Lambda_R$ is over \SI{100}{\dB}. Hence, to fully exploit the R-E advantage of passive beamforming, a large number of reflecting elements are required to enhance the auxiliary channel strength. Another explanation is that the RF-chains of active antennas provide design flexibility in the frequency domain, while the frequency-flat characteristic of the IRS restricts its benefit for broadband transmission, especially when $L$ is small.
		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=0.9\columnwidth}
				\input{assets/re_irs_1mhz.tex}
			\end{adjustbox}
			\caption{Average R-E region for ideal, adaptive, fixed and no IRS over $B=1\,\si{\MHz}$ for $M=1$, $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
			\label{fi:re_irs_1mhz}
		\end{figure}
